---
title: "Week3_Assignment"
author: "Matt Mecoli"
date: "9/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Environment

Loading in relevant packages and setting up environment.

```{r environment}
library(tidyverse)
```

## Data Import

Importing data into a dataframe.

```{r data_import}
college_majors = read.csv("data/majors-list.csv") 
```

## Assignment Questions

Code for answering the specific questions for this assignment.

### Question 1

Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r question_1}
MajorVec <- as.vector(college_majors$Major)
str_detect(MajorVec, "DATA|STATISTICS")
```

### Question 2

 Write code that transforms the data below into a vector.

```{r question_2}
vector_output <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange" [5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  [9] "elderberry"   "lime"         "lychee"       "mulberry"    [13] "olive"        "salal berry"'

test_str <- str_replace_all(vector_output, "[:cntrl:]|[:digit:]|\\[|\\]",' ')
test_str2 <- str_replace_all(test_str, " \\\"", ' ')
test_str3 <- str_replace_all(test_str2, "\\s+", ' ')
test_str4 <- str_replace_all(test_str3, "\"\\s", '_')
test_str5 <- str_replace_all(test_str4, "\"", '')
test_str6 <- str_trim(test_str5)
back_to_vector <- c(str_split(test_str6, '_'))[[1]]
back_to_vector

```

### Question 3

Describe, in words, what these expressions will match:

1.	(.)\1\1 Will match to the character appearing three times in a row. Ex. 111
2.	“(.)(.)\2\1” Will match to a palindrome of type 1,2,2,1.
3.	(..)\1 Will match any group of two characters repeated once. Ex. 1212
4.	“(.).\1.\1” Backreferences refer to the indicated referenc characters. So a character, followed by any character, follow by the first character, followed by any character, followed by the first character. Ex. 12131.
5.	"(.)(.)(.).*\3\2\1" Three of any chracters follow by any number of other characters and then the first three characters in reverse positional order. So like 123banana321.


### Question 4

Construct regular expressions to match words with certain criteria.

1.	“^(.)(.*\1$) "
The chracter we want in the first position followed by any number of characters and then the character in the last position.
2.	“([A-Za-z][A-Za-z]).*\1”
So any alpha character followed by any alpha character, followed by any number of other characters, followed by the original two alpha characters repeated once.
3.	“([A-Za-z]).\1.\1”
Any alpha chracter followed by any other characters, followed by the first, follow by any number, followed by the first.
